%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}
\title{BrianTQuinnPhDcoverletter}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Brian T.}{Quinn, Ph.D.}
\address{Seattle, WA, 98118}
\mobile{(347)604-2921} 
%%% Social
\email{btquinn@gmail.com}
\homepage{briantquinn.com}
\github{btq}
\linkedin{btqphd}
%%% Optionals
\position{Data Scientist{\enskip\cdotp\enskip}Neuroscientist}
\quote{Curious innovator specializing in data wrangling, data analysis and data visualization.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Bill \& Melinda Gates Foundation}
  {500 Fifth Avenue North, Seattle, WA 98109
}
\letterdate{\today}
\lettertitle{Job Application for Data Analyst, K-12 Strategy and Measurement}
\letteropening{Dear  Recruiting Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Brian T. Quinn, Ph.D.~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
%\cvparagraph{About Me}
%Opening paragraph: State why you are writing; how you learned of the organization or position and basic information about yourself.
I found your job posting for Data Scientist on Glassdoor. I earned my Ph.D. in Neuroscience from New York University and recently completed a data scientist fellowship at The Data Incubator. My skill set is based in distilling insights from huge data sets and crafting them into solutions. I believe I would be an excellent fit for the position.  

%%2nd paragraph: Tell why you are interested in the employer or type of work the employer does(Simply stating that you are interested does not tell why, and can sound like a form letter). Demonstrate that you know enough about the employer or position to relate you background to the emploer or position. Mention specific qualifications which make you a good fit for the employer's needs. (Focus on what you can do for the employer, not what the employer can do for you). This is an opportunity to explain in more detail relevant items in your resume. Refer to the fact that your resume is enclosed. Mention other enclosures if such are required to apply for a position.
As the most-used and most trusted digital transaction management network, DocuSign serves more than 50 million users. With that many users, there is great value in analyzing the data generated by customers as they use and seek support for services. Determining which interactions with customer support are most common, and predicting when they are likely to occur will aid in making efficient staffing decisions. I believe a skilled data scientist like myself can provide these insights and more. 
%What will you do?
%    DocuSign is looking for a mid-level Data Scientist to drive customer insights that impact staffing efficiencies and forecasting, knowledge, training and deflection, product insights as well as customer experience. As the department closest to the customer, your created outputs would influence not just customer support and experience orgs, but are valued and acted on by Product and other leadership as well.
%    Create and execute plans to answer customer support’s most pressing questions. This includes forecasting volume, identifying product enhancements or content that will deflect calls, and quantify of the value that each contact provides in terms of future product adoption or churn reduction.
%    Drive efficiencies in the business with automation of data and information where possible
%    Identify areas of opportunity where existing data could provide business benefit
%    Communicate findings to non-technical audiences through the use of well-designed visualizations and non-technical language
%    Work with data scientists on other teams to identify opportunities for shared work and to create a body of shared understanding and ways of framing the data.



%\cvparagraph{Why Me?}
I am fluent in Python, R, and SQL and am well-versed in conducting hypothesis testing and statistical modeling. I have experience in implementing machine learning techniques to solve real-world problems such as:
\begin{itemize}
  \item Developing software that automatically detects the location of abnormal brain tissue in MRIs
  \item Analyzing New York City Health Department Inspection data for violation trends that could be used to focus future inspections where violations are likely.
  \item Employing natural language processing (NLP) methods to predict Yelp star ratings based on reviewers’ text entries, gaining valuable insights that businesses could use to make staffing, budget, and investment decisions
  \item Analyzing the social network of New York City socialites by scraping the New York Social Diary website for persons appearing in photos together and creating an interactive graph visualization of these connections
\end{itemize}

In addition to my technical proficiency, I have extensive experience communicating my findings to a range of audiences. Whether I am speaking to fellow data scientists on my team, busy physicians who just want results, or undergraduate freshmen, I strive to make data digestible, exciting, and relevant. In my personal life, my commitment to sharing knowledge has led me to volunteer as a math teacher with The Fortune Society, an organization that helps people successfully re-enter society after incarceration. I also enjoy teaching in my neighborhood as a volunteer canoe instructor at the North Brooklyn Community Boathouse.

%3rd paragraph: Indicate that you would like the opportunity to interview for a position or to talk with the employer more about their opportunities or hiring plans. State what you will do to follow up, such as telephone the employer within two weeks. If you will be in the employer's location and could offer to schedule a visit, indicate when. State the you will be glad to provide the employer with any additional information needed. That the employer for her/his consideration
%    Work with data scientists on other teams to identify opportunities for shared work and to create a body of shared understanding and ways of framing the data.
I would be excited to be a Data Scientist at DocuSign to use my skill set to generate and support ideas that optimize customer experience. It is clear to me that DocuSign's focus on innovation, collaboration, and data analytics align with my skill and interests. \textbf{I am in Seattle until February 24th} and I encourage you to reach out to me for a conversation during this time. I thank you for your consideration and hope we will have the opportunity to discuss my qualifications in person.
%DocuSign is looking for a mid-level Data Scientist to drive customer insights that impact staffing efficiencies and forecasting, knowledge, training and deflection, product insights as well as customer experience. As the department closest to the customer, your created outputs would influence not just customer support and experience orgs, but are valued and acted on by Product and other leadership as well.
\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
